A Test of the Frequency Independence Assumption of Power System Parameters used in Geomagnetically Induced Current Estimates

### 2019-04-08 paper.tex

\documentclass[draft,linenumbers]{agujournal2018}
\usepackage{apacite}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage[colorlinks]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{framebox}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_H-options-1.pdf}
\caption{Impulse responses for the parameters in Models 1, 2, and 4. The circles at $t$ $=0$ correspond to the impulse response for Model 1; the red/blue lines are the impulse responses for Model 2 and 4. The values of $\overline{a}_o$ and $\overline{b}_o$ reduced by a factor of 10.}
\label{H}
\end{figure}

\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1.pdf}
\caption{Frequency domain transfer functions for the parameters in Models 1, 2, and 4. The frequency domain transfer functions for $a_o$ and $b_o$ in Model~1 are constant and equal to $a_o$ and $b_o$.}
\label{Z}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Phi-options-1.pdf}
\caption{Frequency domain phase values for the parameters in Models 1, 2, and 4. The phase for $a_o$ and $b_o$ are constant either 0 or 180 degrees depending on the sign of their value, with positive values having a phase of 0.}
\label{Phi}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z_MT-options-1.pdf}
\caption{Frequency domain transfer functions for the parameters in Model~3.}
\label{Z_MT}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Phi_MT-options-1.pdf}
\caption{Frequency domain phase values for the parameters in Model~3.}
\label{Phi_MT}
\end{figure}

>>>>

\documentclass[draft,linenumbers]{agujournal2018}
\usepackage{apacite}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage[colorlinks]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

%\usepackage{framebox}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z-options-1.pdf}
\caption{Frequency domain transfer functions for the parameters in Models 1, 2, and 4. The frequency domain transfer functions for $a_o$ and $b_o$ in Model~1 are constant and equal to $a_o$ and $b_o$.}
\label{Z}
%\end{figure}

\vspace{4em}

%\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Phi-options-1.pdf}
\caption{Frequency domain phase values for the parameters in Models 1, 2, and 4. The phase for $a_o$ and $b_o$ are constant either 0 or 180 degrees depending on the sign of their value, with positive values having a phase of 0.}
\label{Phi}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Z_MT-options-1.pdf}
\caption{Frequency domain transfer functions for the parameters in Model~3.}
\label{Z_MT}
%\end{figure}

\vspace{4em}

%\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{figures/plot_model_summary_Phi_MT-options-1.pdf}
\caption{Frequency domain phase values for the parameters in Model~3.}
\label{Phi_MT}
\end{figure}
